Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-07 ms.tex
we dont believe you

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}} \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
\times 10^6\ \, v_{500}^2 \,\,{\rm K},
\label{eq:Tanalytic}
\end{align}
{\bf AG missing correction here for black hole velocity dispersion}
where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$).  Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
  \rs=\frac{G \Mbh}{\densSlope
    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
\label{eq:stag_analytic}
\end{align}
where $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
density power-law slope at $r = r_{\rm s}$. We find that

\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

>>>>

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}} \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p \tilde{v}_{w}^{2}}{2k} \approx 3.7
\times 10^6\ \, v_{500}^2 \,\,{\rm K},
\label{eq:Tanalytic}
\end{align}
where $v_{500} \equiv \tilde{v}_{w}/(500$ km s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm s}}$ is the
density power-law slope at $r = r_{\rm s}$ {\bf BDM: FIXXXX T equation!!}.  Empirically, we find that 
\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
  \rs=\frac{G \Mbh}{\densSlope
    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
\label{eq:stag_analytic}
\end{align}
